Turbulence in compact to giant HII regions

### 2022-02-22 Corr.tex
Javier changes 2022-02-22

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
 log $\sigma$ &            log L(H) &   0.28 $\pm$ 0.1 &  -9.87 $\pm$ 3.66 &   0.85 &  0.002 \\
    log $r_0$ &             log $S$ &   0.73 $\pm$ 0.24 &  -1.17 $\pm$ 0.5 &   0.84 &  0.003 \\
 log $\sigma$ &  log $\sigma_{LOS}$ &   0.76 $\pm$ 0.48 &  -0.14 $\pm$ 0.54 &   0.66 &   0.04 \\
      log $m$ &            log dist &  -0.11 $\pm$ 0.08 &   1.21 $\pm$ 0.16 &  -0.59 &   0.07 \\
 log $\sigma$ &         log $r_{0}$ &   0.22 $\pm$ 0.18 &   0.65 $\pm$ 0.12 &   0.55 &  0.10 \\
      log $m$ &        log $\sigma$ &  -0.14 $\pm$ 0.24 &   0.11 $\pm$ 0.18 &  -0.42 &  0.22 \\
      log $m$ &         log $r_{0}$ &  -0.04 $\pm$ 0.08 &   0.01 $\pm$ 0.05 &  -0.39 &   0.27 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
 log $\sigma$ &            log L(H) &   0.29 $\pm$ 0.09 &  -10.24 $\pm$ 3.53 &   0.89 &  0.001 \\
    log $r_0$ &             log $S$ &   0.78 $\pm$ 0.25 &   -1.31 $\pm$ 0.52 &   0.85 &  0.002 \\
% log $\sigma$ &  log $\sigma_{LOS}$ &   0.83 $\pm$ 0.48 &   -0.24 $\pm$ 0.56 &   0.71 &   0.02 \\
 log $\sigma$ &         log $r_{0}$ &   0.21 $\pm$ 0.17 &    0.66 $\pm$ 0.12 &   0.58 &   0.08 \\
      log $m$ &            log Dist &  -0.09 $\pm$ 0.07 &    1.14 $\pm$ 0.14 &  -0.57 &   0.09 \\
      log $m$ &        log $\sigma$ &  -0.11 $\pm$ 0.21 &    0.07 $\pm$ 0.16 &  -0.42 &   0.23 \\
      log $m$ &         log $r_{0}$ &  -0.04 $\pm$ 0.07 &    -0.0 $\pm$ 0.05 &  -0.39 &   0.26 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

### 2022-02-22 strucfunc_paper.tex
Javier changes 2022-02-22

We present our second-order structure results plotted against separation in parsecs and the posteriors of the parameters used in the analysis we describes in the previous section.

@@

Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig. \ref{fig:velocity-maps}. The solid circles indicate the range use in the non-linear regression analysis (see section~\ref{sec:methods-apply}), while the open circles are the points of the structure function that where left out.
This was done to enhance the possibilities of a convergence since the structure function values at large separations are to follow the 2\(\sigma^2\) value according to theory.
The light shaded areas in the plots show where the separation \(r\) is above half of the box size \(L\), which is indicated with a vertical dotted line.

@@

Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} right panels show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints. 
These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
They also show the marginalized distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.

The results shown on left panels on Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} show a typical second-order structure function pattern, where there is a series of ascending values of  the structure function that tends to stabilize around the 2\(\sigma^2\) value, indicating a loss in the correlations at large separations. 
The Carina nebula and Hubble X follow this behavior.

For astronomical observations it is thought that the values at large separations not following the previous pattern reflects movements that are not related to the ionized gas random motions.
It is known that HII regions are created on the edge of molecular clouds, so they will reach a blister or champagne phase, introducing large-scale gradients \citep{Mivi1995}. 
Also there is the expansion or rotation of each region.

A more common pattern for structure functions of HII regions looks like a 'hook' where at large separations the structure function values start decreasing.
This behavior is shown in the Orion core, 30 Doradus, Hubble V, NGC 595 and the EON.
Less common is the behavior where at large separations there are also a series of ascending values in the structure function, like the Lagoon nebula or NGC 346, or a periodic behavior like NGC 604.

Table \ref{tab:Res} presents the turbulent parameters results along the obtained observational constraints.

The second column correspond to the true variance \(\sigma^2\pos\) of the velocity field.
For all regions except for Carina, Lagoon and the EON there is an increase in this value.
For 30 Doradus, which has the highest value, \(\sigma\) goes from \SI{16}{km.s^{-1}} to  \SI{19}{km.s^{-1}}.
This is two times higher than NGC 604 that has a change of \SI{7}{km.s^{-1}} to \SI{9}{km.s^{-1}}, followed by NGC 595 with \SI{6.6}{km.s^{-1}} to \SI{7.5}{km.s^{-1}}.
NGC 346 is next with a value of \SI{6}{km.s^{-1}} which is close to the value of the centroid velocities.
Carina presents a value of \SI{4.2}{km.s^{-1}} which is the same as the velocity sample.
The Orion core has a change from \SI{3}{km.s^{-1}} to \SI{4}{km.s^{-1}}.
Hubble X has a value of \SI{3.9}{km.s^{-1}} which is very close with respect the \SI{3.6}{km.s^{-1}} value of the velocity field.
The value for Hubble V increase from \SI{2.8}{km.s^{-1}} to \SI{3.3}{km.s^{-1}}.
Lagoon presents a value of \SI{2.6}{km.s^{-1}} and the EON value decrease from \SI{3.2}{km.s^{-1}} to \SI{2.2}{km.s^{-1}}.
The \(B_{\text{noise}}\) value is shown in the third column which would be the minimum squared velocity difference that could be measure by the instrument.

The third column in Table \ref{tab:Res} shows the seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
The forth column shows the correlation value \(r_0\) in parsecs.
The \(r_0\) range covered in our results for the sample goes from 0.09 to 12 pc.
The fifth column indicates the size of each observational box in parsecs.
The index \(m\) is shown in the last column and the range covered by the power-law index in our HII region sample goes from 0.7 to 1.5.
The implications of these results is further developed on the next section.

@@

\subsection{Interpretation of the turbulent parameters and origins of interstellar turbulence}\label{sec:interpretation-origin}
\textit{Note: Still working on this section}

>>>>

We present the second-order structure results plotted against separation in parsecs and the posteriors of the turbulent parameters.

@@

%structure functions plots descriptions
Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig. \ref{fig:velocity-maps}. The solid circles indicate the range use in the non-linear regression analysis (see section~\ref{sec:methods-apply}), while the open circles are the points of the structure function that where left out.
This was done to enhance the possibilities of a convergence since the structure function values at large separations are to follow the 2\(\sigma^2\) value according to theory.
The light shaded areas in the plots show where the separation \(r\) is above half of the box size \(L\), which is indicated with a vertical dotted line.

@@

%corner plots descriptions
Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} right panels show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints. 
These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
They also show the marginalized distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.

%structure functions descriptions
On Figures \ref{fig:strucfunc-fit-OrionS}a-\ref{fig:strucfunc-fit-OrionLH}a we see that the second-order structure functions for our sample of \hii{} regions follows the patterns describe in Figure~\ref{fig:model-strucfunc}.
For simplicity, in the next paragraphs where we describe the structure functions of our sample, the small scales would refer to the separations \(r < r_0\) and large scales would refer to separations \(r > r_0\).

Figure~\ref{fig:strucfunc-fit-OrionS}a shows that the structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
Small scales are consider above the separation of \SI{0.002}{pc} (\(s_0\)=\SI{2}{\arcsecond}), which only affects the first point.
From there until separations of \SI{0.003}{pc} all points within this range fall below the true model showing that they affected at some extent by the seeing. 
The correlation length for the Orion core is 0.07\(\pm\)0.01 pc with a \(\sigma^2\pos\) of 13\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
At large scales there is a small plateau around \SI{22}{km^{2}.s^{-2}} reached at \SI{0.25}{pc}.
Above separations of \SI{0.3}{pc} the structure function decays a separation of \SI{0.5}{pc} with a value of \SI{7}{km^{2}.s^{-2}}.

In the Figure~\ref{fig:strucfunc-fit-M8}a we see that the Lagoon nebula presents some particular behavior at small and large scales. 
At small scales, considered above the separation of \SI{0.005}{pc} (\(s_0\)=\SI{0.83}{\arcsecond}), the structure function shows the characteristic ascending values despite not being as uniform as the other regions.
In this case there aren't points affected by the seeing.
However, there is a clear tendency of a power-law behavior that fits our model with a \(r_0\) of 1\(\pm\)0.2 pc and a \(\sigma^2\pos\) of 7\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
At large scales there is an indication of some periodic behavior with a very large amplitude of ascending \(B(r)\) at largest separation.
The first maximum value of \(B(r)\) is \(\sim\)\SI{14}{km^{2}.s^{-2}} at a separation of \(\sim\)\SI{2.5}{pc}. 
Then at \(\sim\)\SI{4.5}{pc} the minimum value, \(\sim\)\SI{11}{km^{2}.s^{-2}}, of the first oscillation is reached.
From this point the structure function keeps going up until it reaches \SI{66}{km^{2}.s^{-2}} at \SI{20}{pc}.

At small scales the Carina structure function, Figure~\ref{fig:strucfunc-fit-CarC}a, shows the most erratic behavior of all our sample.
Despite this lack of uniformity, still it is possible to see a series of ascending values indicating the existence of correlations in the velocity field that fits our proposed model.
The seeing is \SI{0.008}{pc} (\(s_0\)=\SI{1.3}{\arcsecond}) and there aren't any points that lie below the true model as in the Lagoon nebula.
The correlation length is 0.56\(\pm\)0.04 pc at a \(\sigma^2\pos\) of 18\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
At larges scales the structure function of the Carina nebula follows a pattern that closely resembles the homogeneous fluctuation of Figure~\ref{fig:model-strucfunc}a.
The structure function reaches a plateau around \SI{36}{km^{2}.s^{-2}} at \(\sim\) \SI{2}{pc}.
When \(r >\)\SI{6}{pc} the structure functions resembles a periodic behavior with a small amplitude.

For Carina and Lagoon nebula, the velocity fields are obtained from the FLAMES multi-fiber instrument (section~\ref{sec:flames-multi-fiber}). 
We can see from Figure~\ref{fig:velocity-maps} that observations from this instrument do not give uniform maps as the other instruments. 
Instead the discrete fiber positions are diversely located across the FOV.
This would affect the structure function since the values are not adjacent as the other observations.
This is reflected in the non uniform \(B(r)\) values at small scales that we point in the previous paragraphs.

In the Figure~\ref{fig:strucfunc-fit-N346}a we show the structure function of NGC 346.
For this region the points are above the seeing value which is \SI{0.07}{pc} (\(s_0\)=\SI{0.23}{\arcsecond}) but still the first 8 points lie below the true model.
At separations above \SI{0.4}{pc} the structure functions observed values coincide with the true model. 
The correlation length is 2\(\pm\)0.1 pc at a \(\sigma^2\pos\) of 37\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
For larger scales a periodic behavior is seen above \SI{9}{pc} with a \(B(r)\) value of \SI{70}{km^{2}.s^{-2}}.
Starting from a separation of \SI{12}{pc} and a \(B(r)\) value of \SI{65}{km^{2}.s^{-2}} the structure function keeps ascending until it reaches \SI{146}{km^{2}.s^{-2}} at \SI{24}{pc}.

The 30 Doradus structure function is shown in Figure~\ref{fig:strucfunc-fit-Dor}a.
The seeing value for this regions is \SI{0.16}{pc} (\(s_0\)=\SI{0.7}{\arcsecond}) and just one point of the structure function is below this value.
Until a separation of \SI{1.7}{pc} the structure function lies below the true model.
The correlation length is 4\(\pm\)0.2 pc at a \(\sigma^2\pos\) of 300\(\pm\)9 \(\text{km}^2 \text{s}^{-2}\).
As the Orion core, 30 Doradus structure function presents a behavior of tapered fluctuations.  
The maximum \(B(r)\) value is \SI{655}{km^{2}.s^{-2}} at a separation of \SI{21}{pc}. 
From there \(B(r)\) values descends until they reach \SI{250}{km^{2}.s^{-2}} at \SI{38}{pc}.

In the Figure~\ref{fig:strucfunc-fit-HV}a we show the structure function of Hubble V.
The structure function is well behaved with our model and present characteristics of tapered fluctuations with a small periodic behavior.
The value of the seeing for this regions is \SI{0.5}{pc} (\(s_0\)=\SI{0.2}{\arcsecond})..
Despite this seeing value, all the structure function points lies below the true model which would indicate that the seeing is affecting the observed structure function.
The correlation length is 3.4\(\pm\)0.3 pc with a \(\sigma^2\pos\) of 10\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
The maximum \(B(r)\) value is \SI{18}{km^{2}.s^{-2}} at a separation of \SI{25}{pc}. 
From there \(B(r)\) values descends until \SI{14}{km^{2}.s^{-2}} at \SI{45}{pc}, there is a rise in \(B(r)\) for the next point at \SI{50}{pc} with a value of \SI{15}{km^{2}.s^{-2}} and finally the structure functions descends at \SI{9}{km^{2}.s^{-2}} for a separation of \SI{70}{pc}.

The Hubble X structure function is shown in Figure~\ref{fig:strucfunc-fit-HX}a.
The seeing is \SI{0.006}{pc} (\(s_0\)=\SI{0.24}{\arcsecond}) and as in Hubble V the observed structure function lies below the true model.
The correlation length is 4\(\pm\)0.4 pc at a \(\sigma^2\pos\) of 16\(\pm\)1 \(\text{km}^2 \text{s}^{-2}\).
The structure functions presents at large scales the behavior of periodic fluctuations.
A plateau is reached around \SI{25}{km^{2}.s^{-2}} at a separation of \SI{14}{pc} and a maximum \(B(r)\) value of \SI{31}{km^{2}.s^{-2}} at a separation of \SI{36}{pc}. 
From this point the structure functions shows consistent values around \SI{24}{km^{2}.s^{-2}} and finally there is a rise in \(B(r)\) to \SI{29}{km^{2}.s^{-2}} at a separation of \SI{91}{pc}.

In the Figure~\ref{fig:strucfunc-fit-N595}a we show the structure function of NGC 595.
The seeing is \SI{0.5}{pc} (\(s_0\)=\SI{0.12}{\arcsecond}) and for this region only the first point is below the true model and starting from \SI{2}{pc} there is a good agreement between the observed structure function.
The correlation length is 12\(\pm\)1 pc at a \(\sigma^2\pos\) of 56\(\pm\)2 \(\text{km}^2 \text{s}^{-2}\).
At large scales the structure function behave following the tapered fluctuations behavior.
A maximum \(B(r)\) value of \SI{104}{km^{2}.s^{-2}} is reached at \SI{33}{pc}. 
From there the structure functions decays following and inhomogeneous pattern until it reaches \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.

Table \ref{tab:Res} presents the turbulent parameters results along the obtained observational constraints mentioned in the paragraphs above.
The second column correspond to the variance \(\sigma^2\pos\) of the velocity field.
The \(B_{\text{noise}}\) value is shown in the third column which would be the minimum squared velocity difference that could be measure by the instrument.
The forth column in Table \ref{tab:Res} shows the seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
The fifth column shows the correlation value \(r_0\) in parsecs.
The \(r_0\) range covered in our results for the sample goes from 0.09 to 12 pc.
The sixth column indicates the size of each observational box in parsecs.
The index \(m\) is shown in the last column and the range covered by the power-law index in our HII region sample goes from 0.7 to 1.5.
The interpretation of our results is developed in the next section.

@@

\subsection{Interpretation of the turbulent parameters and origins of interstellar turbulence}\label{sec:interpretation-origin}
